\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 coqimpl.tex
address a comment

The type of \lsti{STLC\_env}'s \lsti{self} parameter is \lsti{STLC\_env\_Ctx},
a module type constructed from \lsti{STLC\_ty}, 
the translation of the field before \lsti{env},
and its context \lsti{STLC\_ty\_Ctx}\EDJ{Why I see in the figure there are only two includes, i.e. only stlcty and stlctyctx}.
In turn, \lsti{STLC\_ty\_Ctx} (not shown in \cref{fig:stlc-compiled}) is
constructed from \lsti{STLC\_subst},
the translation of the field before \lsti{ty},
and its context \lsti{STLC\_subst\_Ctx}.
Thus, the \lsti{self} parameter can be used to reference those and only
those fields in the current field's typing context, which echoes the
discussion in \cref{sec:sound}.

@@

An \lsti{FInductive} definition is translated to a parameterized module type.
Consider the inductive type \lsti{tm}.
In \lsti{STLC}, it is translated to a top-level module type
\lsti{STLC\_tm} that declares a \lsti{tm} type,
its constructors (e.g., \lsti{tm_abs}) \EDJ{I am not sure if it is better we emphasize in the following way :`` that declares a tm type, its constructors (e.g. tmabs) as a normal function,.. '' i.e. emphasize it is a normal function in the module type},
its partial recursor (\lsti{tm_prect_STLC}),
and the propositional equalities on the partial recursor
(e.g., \lsti{tm_abs_eq_STLC}; \cref{sec:prec}).

Importantly,
\lsti{STLC\_tm} merely declares the existence of these names and their types;\EDJ{What does this sentence mean?}
it does not specify their definitions or proofs.
Knowing the existence of these names and their types
suffices to type-check and translate the rest of the family.
Leaving the definitions and proofs open enables \lsti{STLC} and \lsti{STLCFix}
to instantiate \lsti{tm} differently upon \lsti{End}~\lsti{STLC} and \lsti{End}~\lsti{STLCFix}.

>>>>

The type of \lsti{STLC\_env}'s \lsti{self} parameter is \lsti{STLC\_env\_Ctx},
a module type constructed from \lsti{STLC\_ty}, 
the translation of the field before \lsti{env},
and its context \lsti{STLC\_ty\_Ctx}.
In turn, \lsti{STLC\_ty\_Ctx} (not shown in \cref{fig:stlc-compiled}) is
constructed from \lsti{STLC\_subst},
the translation of the field before \lsti{ty},
and its context \lsti{STLC\_subst\_Ctx}.
Thus, the \lsti{self} parameter can be used to reference those and only
those fields in the current field's typing context, which echoes the
discussion in \cref{sec:sound}.

@@

An \lsti{FInductive} definition is translated to a parameterized module type.
Consider the inductive type \lsti{tm}.
In \lsti{STLC}, it is translated to a top-level module type
\lsti{STLC\_tm} that declares a \lsti{tm} type,
its constructors (e.g., \lsti{tm_abs}),
its partial recursor (\lsti{tm_prect_STLC}),
and the propositional equalities on the partial recursor
(e.g., \lsti{tm_abs_eq_STLC}; \cref{sec:prec}).

Importantly,
\lsti{STLC\_tm} merely declares the existence of these names and their types;
it does not specify their definitions.
Having these names and their types available through the context parameters (\lsti{self})
suffices for the translations of the subsequent fields to be type-checked by Coq.
Leaving the definitions open enables \lsti{STLC} and \lsti{STLCFix}
to instantiate \lsti{tm} differently upon \lsti{End}~\lsti{STLC} and \lsti{End}~\lsti{STLCFix}.
